Manuscript

### 2017-07-19 manuscript.Rmd
Edits during the call with Kari

@@

Calculate the logsum given the tracts and parks dataset:
```{r accessibility}
regression_data[[1]]["park_ls"] <- calculate_park_logsums(
  denver_tracts, denver_parks, betas = c(.00001, -5))
regression_data[[2]]["park_ls"] <- calculate_park_logsums(
  boston_tracts, boston_parks, betas = c(.00001, -30))
regression_data[[3]]["park_ls"] <- calculate_park_logsums(
  nyc_tracts, nyc_parks, betas = c(.00001, -5))
```

Create regression equations for use in spatial econometric models:
```{r regression_eq}
base_formula <- formula(
  ~ Income1 + Income2 + Income3 + Income4 + Income5 + Income6 + Income7 + 
    Income8 + Income9 + Income10 + log(Pop_Density) + FulltimeWork + 
    CollegePercent + SinglePercent + Pct0to17 + Pct18to29 + Pct30to64 + 
    Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + 
    PctOther + PctHispanic)

@@

Locate the centroid of all parks and all census tracts and create a distance matrix:
```{r distancematrix}
# why are we computing the distance matrices if we are using contiguity-based
# neighbors?
tract_centroids <- lapply(seq_along(1:length(cities)), function(i){
  gCentroid(tract_shapes[[i]], byid = TRUE)
})

@@

```{r sem}
base_sem <- lapply(seq_along(1:length(dependent_variables)), function(dv){
  this_formula <- substitute(update(base_formula, x ~ .), 
                             list(x = as.name(dependent_variables[dv]) ))

@@

mc_impacts <- lapply(base_sdm, function(dv){
  # TODO
  impacts <- lapply(seq_along(1:1), function(i) {
    impact_summary(summary(impacts(dv[[i]], tr = tr_mc[[i]], R = 500, empirical = TRUE)))
  })

@@

htmlreg(denver_obesity_models, caption = "Denver: Models of Obesity Prevalence")
```

>>>>

```{r}
denver_plots <- spTransform(denver_tracts, CRSobj = CRS("+init=epsg:4326"))
library(leaflet)
leaflet() %>%
  addTiles() %>%
  addPolygons(data = denver_plots)
```

@@

Calculate the logsum given the tracts and parks dataset:
```{r accessibility}
regression_data[[1]]["park_ls"] <- calculate_park_logsums(
  denver_tracts, denver_parks, betas = c(.00001, -5))
# regression_data[[2]]["park_ls"] <- calculate_park_logsums(
#   boston_tracts, boston_parks, betas = c(.00001, -30))
# regression_data[[3]]["park_ls"] <- calculate_park_logsums(
#   nyc_tracts, nyc_parks, betas = c(.00001, -5))
```

Create regression equations for use in spatial econometric models:

We looked at income and it doesn't matter.
```{r regression_eq}
base_formula <- formula(
  ~ log(Pop_Density) + FulltimeWork + 
    CollegePercent + SinglePercent + Pct0to17 + Pct18to29 + Pct30to64 + 
    Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + 
    PctOther + PctHispanic)

@@

Locate the centroid of all parks and all census tracts and create a distance matrix:
```{r distancematrix, eval = FALSE}
# why are we computing the distance matrices if we are using contiguity-based
# neighbors?
tract_centroids <- lapply(seq_along(1:length(cities)), function(i){
  gCentroid(tract_shapes[[i]], byid = TRUE)
})

@@

A likelihood ratio test of the SDM and SEM revealed that the SDM is more likely.

```{r sem, eval = FALSE}
base_sem <- lapply(seq_along(1:length(dependent_variables)), function(dv){
  this_formula <- substitute(update(base_formula, x ~ .), 
                             list(x = as.name(dependent_variables[dv]) ))

@@

mc_impacts <- lapply(park_sdm, function(dv){
  # TODO
  impacts <- lapply(seq_along(1:1), function(i) {
    impact_summary(summary(impacts(dv[[i]], tr = tr_mc[[i]], R = 500, empirical = TRUE)))
  })

@@

screenreg(denver_obesity_models, caption = "Denver: Models of Obesity Prevalence")
```
